Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-08-14 manuscript.Rmd
Working on revision

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021]. The primary advantage of video recording is that it captures real-time behavior.Standard 30 Hz video recording is adequate to capture changes in infant body position that occur on the timescale of seconds. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. An experimenter cannot follow behind infants to record their behavior from morning to night; typical video recording sessions last 45-120 minutes [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021], far short of capturing the variety of activities across the full daily routine. Even if full-day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation would be immense. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full "waking day" of approximately 11 hours for a 12-month-old [@GallandTaylor2012] could take 22-55 hours of labor to annotate.

@@

The open question is whether *automatic classification* is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurements continue to be accurate over long recording periods. Data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration time series) into meaningful categories. Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is a complex because movement can vary greatly *within* a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant can be stationary in "tummy time", or they can crawl in a myriad of ways [@AdolphVereijken1998]. Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a "V" position with legs fully extended, or in a "W" position with knees bent. Sitting on a caregiver's lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity [@KwonZavos2019; @PatelShi2019].

@@

Accordingly, the overarching goal of the current study is to test the validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022], whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Prior work focused on "free play", in which caregivers were asked to play with the infant without restraining the infant or otherwise shaping how they could move. However, in a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. For example different types of sitting---independently on the floor, supported on a caregiver's lap, or restrained in a high chair---all need to be scored as sitting. Moreover, classifiers must be able to detect new variants of behaviors that might arise over the course of a real day; it is impossible for researchers to gather training data for every possible variation that might occur. Thus, our central question is whether models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time? Assessing the validity of temporally *distal* periods---when infants and caregivers are unsupervised and free to follow their everyday routines---is a crucial step to establish whether automatic classification can be used to measure body position across a day.

@@

Four inertial movement units (IMUs) were used to record infant movement across the day (MC10 Biostamp). A custom garment was designed to hold the IMUs: Internal pockets were sewn into snug-fitting infant leggings so that IMUs would stay close to the body (reducing vibration). A pocket over the thigh and a pocket just above the ankle were sewn on the lateral surface of the right and left legs of the garment. Multiple sizes of the garment were created (modeled on US 3-6 mo, 6-9 mo, 9-12 mo, and 12-18 mo sizing). Caregivers indicated in advance which size would fit their infant, and to "size down" if between sizes to ensure a snug fit and minimize sensor movement. Each garment had a distinct pattern on the seat of the pants so that caregivers could identify front versus back and place the garment in the correct orientation.

Each sensor had sufficient battery and onboard torage to record accelerometer and gyroscope data for approximately 12 hours. We chose a sampling rate of 62.5 Hz (one of the available presets) based on prior work that used rates of 50-64 Hz [@FranchakScott2021; @AiraksinenRasanen2020; @YaoPlotz2019]. Infants also wore a LENA&reg; recorder throughout the day in the front pocket of a LENA&reg; shirt, located near the infant’s chest, to determine whether data could be simultaneously recorded from the LENA&reg; and IMU sensors (LENA&reg; data were not analyzed in the current study).

@@

Supine was coded when the infant was lying on their back, on their side, or was reclined up to a 45  Prone was coded when the infant was lying on their stomach, was stationary supported by the hands/knees or the hands/feet, or was crawling. We scored sitting to include any form of the following seated positions: 1) infants sat with their buttocks on a surface, such as on the floor or a caregiver’s lap, 2) infant was in a kneeling-sit position, in which their knees were on the ground with their legs tucked underneath the buttocks, and 3) infant was in a seating device, such as a high chair, that kept the torso oriented perpendicular to the ground (a reclined position, such as in a young infant's car seat, would be counted as supine). Upright was coded when the infant was standing or squatting on the ground with two feet or walking (regardless of whether infants' balance was assisted by a caregiver or with their hands holding onto something for support). Our goal in creating a category for "held by caregiver" was to separate times when infants were in control of their body position from times when they were suspended in the air (rather than resting on furniture or a surface). Held was coded when infants were carried off of the groun. However, when the caregiver was sitting with the infant in their lap the infant’s body position was coded as if the caregiver was a surface (e.g., if the infant was sitting on the caregiver’s lap this was coded as sitting). Times during the video when the infant was out of view were excluded. Periods when the sensor garment was adjusted or taken off the infant were also excluded, as were transitions between body positions.

@@

Classification training and prediction was conducted on a windowed dataset that summarized the raw, 62.5 Hz motion signals within 4-s windows. Data were reduced in time by creating overlapping moving windows (4-s long, comprising 250 samples) starting each second, which is a common unit of analysis in prior studies of human activity classification [@FranchakScott2021; @NamPark2013; @AiraksinenRasanen2020]. For each 4-s window, we aggregated the 250 samples to create single scores for a variety of motion features---summary statistics that could be fed into the machine learning model. The minimum, maximum, 25th percentile, 75th percentile, mean, median, skew, kurtosis, standard deviation, and sum were computed for each signal (e.g., right thigh X linear acceleration, left ankle pitch angular acceleration). The 10 summary statistics and 24 sensor signals generated 240 columns of motion features that described movement within each window. Furthermore, a series of cross-sensor and cross-orientation summaries (such as the correlation, magnitude, and difference between pairs of sensors) added an additional 196 columns of motion features. The 436 total motion features corresponded to a single body annotation code for each 4-s window. Windows were only used for training/testing if they contained a single body position for > 75% (3 s) of time within the window to ensure that motion signals could be linked to an unambiguous example of each behavior.

@@

Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models  (*M* = `r metrics_lookup["Overall Accuracy", "mean_Group"]`) was slightly lower than accuracy for individual models (*M* = `r metrics_lookup["Overall Accuracy", "mean_Individual"]`). Although overall accuracy from our semi-supervised, in-home data collection did not match the near-perfect accuracy  (.95-.98) found in prior in-lab studies [@FranchakScott2021; @AiraksinenRasanen2020], both models approached the level of agreement found between two human coders (*M* = .906). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in a a semi-supervised setting rather than from a difference in the quality of the classification model; although the first part of the proximal period was guided by the experimenter during a brief phone call, the remainder of the proximal period included natural behavior. Visual inspection of Figure \@ref(fig:metrics)A shows that accuracy values were heavily skewed, with many approaching perfect accuracy but a few sessions with very poor accuracy. Looking at the median performance suggests that the difference between models was not considerable for the typical participant (group median accuracy = `r metrics_lookup["Overall Accuracy", "median_Group"]`; individual median accuracy = `r metrics_lookup["Overall Accuracy", "median_Individual"]`).

@@

Among participants who wore the sensors from morning to bedtime, all infants wore the sensor garment during 100% of the intended recording period, excluding the times caregivers were asked to remove the garment (naps, diaper changes, trips out of the house), based on caregiver logs of wear time. No caregiver reporting removing the garment for any other reason (such as infant discomfort), meaning that the majority of the time during the day either resulted in usable body position data or was excluded due to caregiver-reported naps (gray periods in Figure \@ref(fig:timelines)). The total length of the recording period ranged from `r apa_num(min(coverage$total))`-`r apa_num(max(coverage$total))` hours with a median of `r apa_num(median(coverage$total))` hours. Nap times reported during the recording period ranged from `r apa_num(min(coverage$naptime))`-`r apa_num(max(coverage$naptime))` hours with a median of `r apa_num(median(coverage$naptime))` hours. Body position data were available to describe `r apa_num(min(coverage$prop_accounted)*100, digits = 1)`-`r apa_num(max(coverage$prop_accounted)*100, digits = 1)`% of the awake portion of the recording period (median = `r apa_num(median(coverage$prop_accounted)*100, digits = 1)`%). Younger infant \#14 had the least portion of the waking day accounted for; the family left the house to run errands during the majority of the recording period, and the infant napped during much of the remaining time at home. Overall, the recordings produced a median of `r apa_num(median(coverage$hours_recorded))` hours of motion data, with the entire dataset totaling `r apa_num(sum(coverage$hours_recorded))` hours. Even the shortest full recording (`r apa_num(min(coverage$hours_recorded))` hours) exceeded the longest observational sessions in past work in which an experimenter operated a camera.

@@

Figure \@ref(fig:age) shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (*r* = `r age_cor_group["age","upright_time"]`, *p* `r apa_p(age_cor_group_pval["age","upright_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","upright_time"]`, *p* `r apa_p(age_cor_ind_pval["age","upright_time"], add_equals = T)`). Similarly, age predicted increases in sitting time using group (*r* = `r age_cor_group["age","sit_time"]`, *p* `r apa_p(age_cor_group_pval["age","sit_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","sit_time"]`, *p* `r apa_p(age_cor_ind_pval["age","sit_time"], add_equals = T)`). In contrast, age predicted decreases in supine time using group (*r* = `r age_cor_group["age","supine_time"]`, *p* `r apa_p(age_cor_group_pval["age","supine_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","supine_time"]`, *p* `r apa_p(age_cor_ind_pval["age","supine_time"], add_equals = T)`). No clear age trends were found for prone time. Age was not significantly related to held time for group models (*r* = `r age_cor_group["age","held_time"]`, *p* `r apa_p(age_cor_group_pval["age","held_time"], add_equals = T)`), but individual models showed a significant negative correlation (*r* = `r age_cor_ind["age","held_time"]`, *p* `r apa_p(age_cor_ind_pval["age","held_time"], add_equals = T)`) resulting from an outlier in the younger group.

@@

In the past decade, developmental scientists have discovered that distributional information about infants' experiences matter for how infants learn [@ClerkinHart2017; @KachergisYu2017; @RazAbney2019]. Skewed distributions---those that favor the repetition of a small subset of experiences---facilitate learning. For example, recordings from wearable head cameras in the home indicate that infants see a small subset of objects with high frequency [@ClerkinHart2017], but most objects are seen infrequently. Heterogeneity is also found in how experiences are distributed in time---burstiness and clustering are seen in infants' daily experiences seeing objects and hearing music [@MendozaFausey2022; @CasillasElliott2021]. Long-form motor recordings provide a novel opportunity to measure the temporal structure in the sequences of body positions seen in Figure \@ref(fig:timelines). How skewed are infants' experiences with different motor behaviors, and how are they clustered in time? Linking the distributional structure of a particular motor experience in a real day, such as time spent sitting, might be predicted by sitting skill and/or might predict infants' future sitting ability. Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life.@MalachowskiSalo2023 used a combination of LENA&reg; and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA&reg; and long-form motor recordings can take this a step further by measuring more precisely how speech and body position co-vary within a day.

@@

# References

>>>>

Video observation is the most common way of measuring infant motor behavior in home recordings. Most often, an experimenter with a handheld camera follows infants from room to room to ensure that their movements are visible throughout the recording session [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021]. The primary advantage of video recording is that it captures real-time behavior. Standard 30 Hz video recording is adequate to capture changes in infant body position that occur on the timescale of seconds. However, requiring an experimenter to operate a camera is obtrusive, whereas relying on a stationary camera means that infants will be absent from view as they move from place to place. Moreover, video observation cannot easily scale to long durations or large numbers of participants. An experimenter cannot follow behind infants to record their behavior from morning to night; typical video recording sessions last 45-120 minutes [@Karasik2011; @ChenSchneider2022; @HerzbergFletcher2021], far short of capturing the variety of activities across the full daily routine. Even if full-day videos were available, the lack of suitable automatic classification tools means that the human cost of annotation would be immense. Our annotation of body position takes approximately 2-5 hours to complete for every hour of video (depending on how often infants switch positions), meaning that a full "waking day" of approximately 11 hours for a 12-month-old [@GallandTaylor2012] could take 22-55 hours of labor to annotate.

@@

The open question is whether *automatic classification* is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurements continue to be accurate over long recording periods. Data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration time series) into meaningful categories. Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is complex because movement can vary greatly *within* a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant can be stationary in "tummy time", or they can crawl in a myriad of ways [@AdolphVereijken1998]. Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a "V" position with legs fully extended, or in a "W" position with knees bent. Sitting on a caregiver's lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity [@KwonZavos2019; @PatelShi2019].

@@

Accordingly, the overarching goal of the current study is to test the validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022], whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Prior work focused on "free play", in which caregivers were asked to play with the infant without restraining the infant or otherwise shaping how they could move. However, in a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. For example different types of sitting---independently on the floor, supported on a caregiver's lap, or restrained in a high chair---all need to be scored as sitting. Moreover, classifiers must be able to detect new variants of behaviors that might arise over the course of a real day; it is impossible for researchers to gather training data for every possible variation that might occur. Thus, our central question is whether models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time. Assessing the validity of temporally *distal* periods---when infants and caregivers are unsupervised and free to follow their everyday routines---is a crucial step to establish whether automatic classification can be used to measure body position across a day.

@@

Four inertial movement units (IMUs) were used to record infant movement across the day (MC10 Biostamp). A custom garment was designed to hold the IMUs (Figure \@ref(fig:garment)). Internal pockets were sewn into snug-fitting infant leggings so that IMUs would stay close to the body (reducing vibration). A pocket over the thigh and a pocket just above the ankle were sewn on the lateral surface of the right and left legs of the garment. Multiple sizes of the garment were created (modeled on US 3-6 mo, 6-9 mo, 9-12 mo, and 12-18 mo sizing). Caregivers indicated in advance which size would fit their infant, and to "size down" if between sizes to ensure a snug fit and minimize sensor movement. Each garment had a distinct pattern on the seat of the pants so that caregivers could identify front versus back and place the garment in the correct orientation.

Each sensor had sufficient battery and onboard storage to record accelerometer and gyroscope data for approximately 12 hours. We chose a sampling rate of 62.5 Hz (one of the available presets) based on prior work that used rates of 50-64 Hz [@FranchakScott2021; @AiraksinenRasanen2020; @YaoPlotz2019]. Infants also wore a LENA&reg; recorder throughout the day in the front pocket of a LENA&reg; shirt, located near the infant’s chest, to determine whether data could be simultaneously recorded from the LENA&reg; and IMU sensors (LENA&reg; data were not analyzed in the current study).

@@

Supine was coded when the infant was lying on their back, on their side, or was reclined up to a 45 degree angle. Prone was coded when the infant was lying on their stomach, was stationary supported by the hands/knees or the hands/feet, or was crawling. We scored sitting to include any form of the following seated positions: 1) infants sat with their buttocks on a surface, such as on the floor or a caregiver’s lap, 2) infant was in a kneeling-sit position, in which their knees were on the ground with their legs tucked underneath the buttocks, and 3) infant was in a seating device, such as a high chair, that kept the torso oriented perpendicular to the ground (a reclined position, such as in a young infant's car seat, would be counted as supine). Upright was coded when the infant was standing or squatting on the ground with two feet or walking (regardless of whether infants' balance was assisted by a caregiver or with their hands holding onto something for support). Our goal in creating a category for "held by caregiver" was to separate times when infants were in control of their body position from times when they were suspended in the air (rather than resting on furniture or a surface). Held was coded when infants were carried off of the ground. However, when the caregiver was sitting with the infant in their lap the infant’s body position was coded as if the caregiver was a surface (e.g., if the infant was sitting on the caregiver’s lap this was coded as sitting). Times during the video when the infant was out of view were excluded. Periods when the sensor garment was adjusted or taken off the infant were also excluded, as were transitions between body positions.

@@

Classification training and prediction was conducted on a windowed dataset that summarized the raw, 62.5 Hz motion signals within 4-s windows. Data were reduced in time by creating overlapping moving windows (4-s long, comprising 250 samples) starting each second, which is a common unit of analysis in prior studies of human activity classification [@FranchakScott2021; @NamPark2013; @AiraksinenRasanen2020]. For each 4-s window, we aggregated the 250 samples to create single scores for a variety of motion features---summary statistics that could be fed into the machine learning model. The minimum, maximum, 25th percentile, 75th percentile, mean, median, skew, kurtosis, standard deviation, and sum were computed for each signal (e.g., right thigh linear acceleration along the X-axis, left ankle pitch angular acceleration). The 10 summary statistics and 24 sensor signals generated 240 columns of motion features that described movement within each window. Furthermore, a series of cross-sensor and cross-orientation summaries (such as the correlation, magnitude, and difference between pairs of sensors) added an additional 196 columns of motion features. The 436 total motion features corresponded to a single body annotation code for each 4-s window. Windows were only used for training/testing if they contained a single body position for > 75% (3 s) of time within the window to ensure that motion signals could be linked to an unambiguous example of each behavior.

@@

Overall accuracy (Figure \@ref(fig:metrics)A) represents the proportion of 4-s windows in the testing set in which the model prediction matched the human annotation of body position. Overall accuracy for group models  (*M* = `r metrics_lookup["Overall Accuracy", "mean_Group"]`) was slightly lower than accuracy for individual models (*M* = `r metrics_lookup["Overall Accuracy", "mean_Individual"]`). Although overall accuracy from our semi-supervised, in-home data collection did not match the near-perfect accuracy  (.95-.98) found in prior in-lab studies [@FranchakScott2021; @AiraksinenRasanen2020], both models approached the level of agreement found between two human coders (*M* = .906). Most likely, lower accuracy in the current study results from the more variable and complex behavior observed in a semi-supervised setting rather than from a difference in the quality of the classification model; although the first part of the proximal period was guided by the experimenter during a brief phone call, the remainder of the proximal period included natural behavior. Visual inspection of Figure \@ref(fig:metrics)A shows that accuracy values were heavily skewed, with many approaching perfect accuracy but a few sessions with very poor accuracy. Looking at the median performance suggests that the difference between models was not considerable for the typical participant (group median accuracy = `r metrics_lookup["Overall Accuracy", "median_Group"]`; individual median accuracy = `r metrics_lookup["Overall Accuracy", "median_Individual"]`).

@@

Among participants who wore the sensors from morning to bedtime, all infants wore the sensor garment during 100% of the intended recording period, excluding the times caregivers were asked to remove the garment (naps, diaper changes, trips out of the house), based on caregiver logs of wear time. No caregiver reported removing the garment for any other reason (such as infant discomfort), meaning that the majority of the time during the day either resulted in usable body position data or was excluded due to caregiver-reported naps (gray periods in Figure \@ref(fig:timelines)). The total length of the recording period ranged from `r apa_num(min(coverage$total))`-`r apa_num(max(coverage$total))` hours with a median of `r apa_num(median(coverage$total))` hours. Nap times reported during the recording period ranged from `r apa_num(min(coverage$naptime))`-`r apa_num(max(coverage$naptime))` hours with a median of `r apa_num(median(coverage$naptime))` hours. Body position data were available to describe `r apa_num(min(coverage$prop_accounted)*100, digits = 1)`-`r apa_num(max(coverage$prop_accounted)*100, digits = 1)`% of the awake portion of the recording period (median = `r apa_num(median(coverage$prop_accounted)*100, digits = 1)`%). Younger infant \#14 had the least portion of the waking day accounted for; the family left the house to run errands during the majority of the recording period, and the infant napped during much of the remaining time at home. Overall, the recordings produced a median of `r apa_num(median(coverage$hours_recorded))` hours of motion data, with the entire dataset totaling `r apa_num(sum(coverage$hours_recorded))` hours. Even the shortest full recording (`r apa_num(min(coverage$hours_recorded))` hours) exceeded the longest observational sessions in past work in which an experimenter operated a camera.

@@

Figure \@ref(fig:age) shows that both group and individual model predictions captured age-related differences in body position. Age in months and upright time were significantly, positively correlated using group (*r* = `r age_cor_group["age","upright_time"]`, *p* `r apa_p(age_cor_group_pval["age","upright_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","upright_time"]`, *p* `r apa_p(age_cor_ind_pval["age","upright_time"], add_equals = T)`). Similarly, sitting time increased with age based on predictions from both group (*r* = `r age_cor_group["age","sit_time"]`, *p* `r apa_p(age_cor_group_pval["age","sit_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","sit_time"]`, *p* `r apa_p(age_cor_ind_pval["age","sit_time"], add_equals = T)`). In contrast, supine time decreased with age using predictions from both group (*r* = `r age_cor_group["age","supine_time"]`, *p* `r apa_p(age_cor_group_pval["age","supine_time"], add_equals = T)`) and individual models (*r* = `r age_cor_ind["age","supine_time"]`, *p* `r apa_p(age_cor_ind_pval["age","supine_time"], add_equals = T)`). No clear age trends were found for prone time. Age was not significantly related to held time for group models (*r* = `r age_cor_group["age","held_time"]`, *p* `r apa_p(age_cor_group_pval["age","held_time"], add_equals = T)`), but individual models showed a significant negative correlation (*r* = `r age_cor_ind["age","held_time"]`, *p* `r apa_p(age_cor_ind_pval["age","held_time"], add_equals = T)`) resulting from an outlier in the younger group.

@@

In the past decade, developmental scientists have discovered that distributional information about infants' experiences matter for how infants learn [@ClerkinHart2017; @KachergisYu2017; @RazAbney2019]. Skewed distributions---those that favor the repetition of a small subset of experiences---facilitate learning. For example, recordings from wearable head cameras in the home indicate that infants see a small subset of objects with high frequency [@ClerkinHart2017], but most objects are seen infrequently. Heterogeneity is also found in how experiences are distributed in time---burstiness and clustering are seen in infants' daily experiences seeing objects and hearing music [@MendozaFausey2022; @CasillasElliott2021]. Long-form motor recordings provide a novel opportunity to measure the temporal structure in the sequences of body positions seen in Figure \@ref(fig:timelines). How skewed are infants' experiences with different motor behaviors, and how are they clustered in time? Linking the distributional structure of a particular motor experience in a real day, such as time spent sitting, might be predicted by sitting skill and/or might predict infants' future sitting ability. Moreover, real-time recording of motor behavior provides a way to measure how infant motor behavior links to other types of experiences in the moment in daily life. @MalachowskiSalo2023 used a combination of LENA&reg; and EMA surveys to find that infants heard less adult speech when restrained in seating devices. Combining LENA&reg; and long-form motor recordings can take this a step further by measuring more precisely how speech and body position co-vary within a day.

@@

<!-- # References -->
